Title

### 2012-09-12 inc/plasmon/plasmon.tex
further describe the mathematics of plasmons

In order to drive a plasmon on the surface of a material, the portion of the laser wave-vector parallel to the plasmon ($k_{Lx}$) must be matched to the wave-vector of the surface plasmon.
\begin{equation}
  k_{SP} = k_{Lx} + \imath k_{G}
\end{equation}

>>>>

In the grating coupling scheme (shown in \ref{fig:plasmon_schematic}) a laser of wavelength $\lambda$ is incident on a material with a grating of period $d$, making an angle $\theta$ from the surface normal. A surface plasmon is driven when the portion of the laser wave-vector parallel to the plasmon ($k_{Lx}$) and a fourier component ($k_{G} = 2 \pi / d$) of the grating matches the wave-vector of the surface plasmon
\begin{equation}
  k_{SP} = k_{Lx} + n k_{G}
\end{equation}
where $n$ here is an integer.
Which reduces to 
\begin{equation} \label{eq:plasmon_condition}
  \frac{ \varepsilon }{ 1 + \varepsilon } = \sin \theta + \frac{ n \lambda }{ d }
\end{equation}
For a given grating period, \ref{eq:plasmon_condition} determines the angle of incidence that the laser must make with the surface in order to drive the plasmon.
Further, it is used to design the grating, allowing for angles that the microscope column will accept.

\begin{figure}
  \centering
  \input{grating_schematic}
  \caption{Schematic diagram of a grating coupling geometry for driving a surface plasmon}
  \label{fig:plasmon_schematic}
\end{figure}
